Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-21 CMSAC_presentation/CMSAC_reveal_js.qmd
updated method to mathjax.
josie slides updates

## Comparing Structures
::: {.incremental}
-   Which competition structure is best?

@@

@@

-   **Effectivity**[^2]: Interested in correctly ranking the best competitor as first
:::

::: {.fragment}
```{r}
knitr::include_graphics("salient bar.png")
```

@@

## Efficacy and Effectivity

```{r}
knitr::include_graphics("salient examples.png")
```

-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Efficacy: 1 through $n$ matter
    -   Effectivity: 1 is only salient rank

>>>>

## Comparing Structures

-   Which competition structure is best?

    ::: {.incremental}

@@

    - A good tournament: top *k* produced by the tournament matches closely to the true top *k*

::: {.incremental}

-   **Efficacy**: Final rankings should match the true rankings of the strength of the competitors

-   **Effectivity**: Interested in correctly ranking the best competitor as first
:::

## Comparing Structures

-   Which competition structure is best?

    - A good tournament: top *k* produced by the tournament matches closely to the true top *k*

@@

-   **Effectivity**[^2]: Interested in correctly ranking the best competitor as first

@@

## Effectivity and Efficacy

```{r}
knitr::include_graphics("salient bar.png")
```

## Effectivity and Efficacy

```{r, out.width="100%"}
knitr::include_graphics("salient examples.png")
```

::: {.fragment}
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Efficacy: 1 through $n$ matter
    -   Effectivity: 1 is only salient rank
:::
